From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-06-05 dictionary.tex
Added a remark on descent.

@@

\subsection{Descent, revisited}

\begin{proof}
Let $\cs{L}$ be a character sheaf on $G$.
Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.

@@

>>>>

\begin{remark}\label{rem:descent}
In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves $\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see\cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example. 
\end{remark}

@@

@@

\subsection{Descent, revisited}\label{ssec:bS}

\begin{proof}
Objects in $\bCS(G)$ may be described by a small modification to the technique used in Sections~\ref{ssec:E} and \ref{ssec:S}. 
First, recall that

Set $F^{i,j} \ceq C^i_{\text{cts}} (\Gal(\bFq/\Fq), C^j(G(\bFq), \EEx))$

Let $\cs{L}$ be a character sheaf on $G$.
Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.
